A comparison of classification algorithms applied to the Adult Database

### 2009-12-16 demo/demo.tex
added some cluster description.

\frame
{
    \frametitle{Clusters}
}

>>>>

\frame
{
    \frametitle{Clusters}

    \begin{itemize}
    \item<1-> Clustering can be used to detect similar individuals and to build classes in the absence of them.
    \item<1-> Generating 6 clusters with only three variables (\textbf{age}, \textbf{education\_num} and \textbf{hours\_per\_week}) leads to some interesting observations:
    \begin{itemize}
        \item<1-> Younger people are grouped together.
        \item<1-> People with different levels of education belong to different clusters.
    \end{itemize}
    \end{itemize}
}
